---
title: "Soap Analytics"
author: "longhow"
date: "6/19/2018"
output:
  prettydoc::html_pretty:
    highlight: github
    number_sections: yes
    theme: cayman
    toc: yes
    toc_depth: 2
---
# How close are soap episodes to each other?

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(text2vec)
library(dplyr)
library(stringr)
library(reticulate)
library(plotly)
```

## Soap episode summaries 

Import Goede Tijden Slechte Tijden (Dutch soap) and The Bold & Beautiful episode summaries. Categorize episodes into periods of multiple years.

```{r}
GTST = readRDS("data/GTST_samenvattingen.RDs")
BB = readRDS("data/AllBB.RDs")
GTST$season = lubridate::year(GTST$datums2)
GTST$period = cut(GTST$season, breaks = c(1989, 1994, 1998, 2002, 2006, 2010, 2014, 2018))
```

## text mining 

Turn episodes into a term document matrix by applying text mining functions from the `text2vec` library.

```{r}
cleanstring = function(x) {
  x %>% 
    str_to_lower %>% 
    str_replace_all("[^[:alnum:]]", " ") %>% 
    str_replace_all("\\s+", " ")
}

GTST = GTST %>% 
  mutate(
    normalizedText = cleanstring(text_of_1month)
  )

#### tokennize
GTST_tokens = GTST$normalizedText %>% word_tokenizer

#### use the tokens to create an iterator and vocabular
iter = itoken(
  GTST_tokens, 
  ids = GTST$datums2,
  progressbar = TRUE
)

#### remove some Dutch stopwords
stw = stopwords::stopwords( language = "nl")

#### Create vocabulary and prune the dimension
vocab = create_vocabulary(
  iter, 
  stopwords = c(stw,letters),
  ngram = c(ngram_min = 1L, ngram_max = 3L)
)

pruned_vocab = prune_vocabulary(vocab, doc_proportion_min = 0.001 )

#### create document term matrix and tfidf 
vectorizer = vocab_vectorizer(pruned_vocab)
dtm = create_dtm(iter, vectorizer)

#### define tfidf model (Inverse document frequency)
tfidf = TfIdf$new()
# fit model to train data and transform train data with fitted model
dtm_tfidf = fit_transform(dtm, tfidf)

```

Now we have a matrix with dimensions `r dim(dtm_tfidf)` 

## UMAP

Now apply Uniform Manifold Approximation and Projection using the python umap package trough the reticulate library.

```{r}
use_condaenv(condaenv = "test_lhl")
umap = import("umap")

embedding = umap$UMAP(
  n_neighbors = 5L,
  n_components = 3L,
  min_dist = 0.1,
  metric='cosine'
  )

## sparse matrices are not supported to pass on to python
full_dtm = as.matrix(dtm_tfidf)

## compute UMAP with 3 components
embedding_out = embedding$fit_transform(full_dtm)
```

Visualise embedding in 3D with plotly

```{r}
plotdata = data.frame(embedding_out)
plotdata$period = GTST$period
plotdata$season = GTST$season

plot_ly(
  plotdata, 
  x = ~X1,
  y = ~X2, 
  z = ~X3,
  text = ~season,
  color = ~period,
  size = 1, sizes = c(1,3) 
) %>% 
    layout(title = 'Goede Tijden Slechte Tijden samenvattingen geprojecteerd in 3D')
```










